Advice on describing Bayesian analysis of neutron and X-ray reflectometry

### 2022-07-20 src/tex/ms.tex

Reflectometry analysis can be described, in the most simplistic terms, as a comparison and refinement of a model based on some parameters, $\mathbf{x}$, to reproduce some reflectivity data set, $\mathbf{D}$. 
This refinement process involves comparing the model to the data and calculating some goodness-of-fit parameter or likelihood, $p(\mathbf{D} | \mathbf{x})$, and modifying the model to either minimise or maximise this, as appropriate. 
A commonly used goodness-of-fit parameter is the $\chi^2$ parameter which is found as \cite{nelson_refnx_2019}, 
%
\begin{equation}
    \chi^2 = \sum_{q=q_{\text{min}}}^{q_{\text{max}}}{\bigg[\frac{(R(q) - R(q)_{\text{m}})}{\sigma_R(q)}\bigg]^2}, 
\end{equation}
%
where, $R(q)$ and $R(q)_{\text{m}}$ are the measured and modelled reflectivity at a given $q$, the measured momentum transfer vector, and $\sigma_R(q)$ is the uncertainty associated with the measured reflectivity at each $q$ point.
The likelihood is related to the $\chi^2$ parameter, however, a larger likelihood is indicative of better agreement between the model and data, 
%
\begin{equation}
    \ln[p(\mathbf{D} | \mathbf{x})] = -\frac{1}{2} \bigg(\chi^2 + \sum_{q=q_{\text{min}}}^{q_{\text{max}}}\ln{\big[2\pi\sigma_R(q)^2\big]}\bigg).
    \label{equ:likelihood}
\end{equation}
%
The input for this refinement process is the model and some initial parameter values, which may be an absolute value or some parameter range, depending on the refinement algorithm. 
The output is a set of values for $\mathbf{x}$, potentially with associated error bars, where these are present they typically describe a standard deviation from the mean of a Gaussian probability distribution. 
This process implicitly assumes that the data is completely reduced, accounting for all experimental parameters, uncertainties are accurately described and the model can accurately describe the data.

>>>>

Reflectometry analysis can be described, in the most simplistic terms, as a comparison and refinement of a model based on some parameters, $\mathbf{x}$, to reproduce some reflectivity data set, $\mathbf{D}$. 
This refinement process involves comparing the model to the data and calculating some goodness-of-fit parameter or likelihood, $p(\mathbf{D} | \mathbf{x})$, and modifying the model to either minimise or maximise this, as appropriate. 
A commonly used goodness-of-fit parameter is the $\chi^2$ parameter which is found as \cite{nelson_refnx_2019}, 
%
\begin{equation}
    \chi^2 = \sum_{q=q_{\text{min}}}^{q_{\text{max}}}{\bigg[\frac{(R(q) - R(q)_{\text{m}})}{\sigma_R(q)}\bigg]^2}, 
\end{equation}
%
where, $R(q)$ and $R(q)_{\text{m}}$ are the measured and modelled reflectivity at a given $q$, the measured momentum transfer vector, and $\sigma_R(q)$ is the uncertainty associated with the measured reflectivity at each $q$ point. 
Under an assumption of normally distributed residuals $R(q) - R(q)_{\text{m}} \sim \mathcal{N}(0, \sigma_R(q))$, the likelihood is related to the $\chi^2$ variable in the following way:
%
\begin{equation}
    \ln[p(\mathbf{D} | \mathbf{x})] = -\frac{1}{2} \bigg(\chi^2 + \sum_{q=q_{\text{min}}}^{q_{\text{max}}}\ln{\big[2\pi\sigma_R(q)^2\big]}\bigg).
    \label{equ:likelihood}
\end{equation}
%
The input for this refinement process is the model and some initial parameter values, which may be an absolute value or some parameter range, depending on the refinement algorithm. 
The output is a set of values for $\mathbf{x}$, potentially with associated error bars, where these are present they typically describe a standard deviation from the mean of a Gaussian probability distribution. 
This process implicitly assumes that the data is completely reduced, accounting for all experimental parameters, uncertainties are accurately described and the model can accurately describe the data.
